MSF_Groupwork-NBA_shotlog

### 2016-10-09 MSFGroupwork-NBAHotHand.Rmd
completed home/away initial analysis

@@

for (i in 1:nrow(df)) {
  if (df[i,"W"]=="W") df[i,"W"]<- 1
  if (df[i,"W"]=="L") df[i,"W"]<- 0
}

@@

for (i in 1:nrow(df)) {
  df$HOME_TEAM [i] <- unlist(strsplit(df$MATCHUP[i]," "))[5]
  df$AWAY_TEAM [i] <- unlist(strsplit(df$MATCHUP[i]," "))[7]
}
```

```{r}
#combining columns for the analysis
library(reshape)
```

>>>>

#we need to change the format of some of the columns to 'Character'

@@

for (i in 1:nrow(df)) {
  if (df[i,"W"]=="W") df[i,"W"]<- 1
  if (df[i,"W"]=="L") df[i,"W"]<- 0}

@@

for (i in 1:nrow(df)) {
  if (LOCATION[i]=="H") {df$HOME_TEAM [i] <- unlist(strsplit(df$MATCHUP[i]," "))[5]
  df$AWAY_TEAM [i] <- unlist(strsplit(df$MATCHUP[i]," "))[7]
  if (W[i]==1) df$WINNER[i] <- "HOME" 
  if (W[i]==0) df$WINNER[i] <- "AWAY"}
  if (LOCATION[i]=="A") {df$HOME_TEAM [i] <- unlist(strsplit(df$MATCHUP[i]," "))[7] 
  df$AWAY_TEAM [i] <- unlist(strsplit(df$MATCHUP[i]," "))[5]
  if (W[i]==0) df$WINNER[i] <- "HOME"  
  if (W[i]==1) df$WINNER[i] <- "AWAY"}}

df$BLANK<-"" #for some reason cast function does not work with last column in dataframe, so I have created this BLANK column as I need to use AWAY_TEAM colum (it was a last column). 
```

```{r}
#combining columns for the analysis
library(reshape)
dfwl<- cast(df, GAME_ID1 + HOME_TEAM + AWAY_TEAM + WINNER ~ LOCATION)
dfwl[,"WINNER"] <- as.character(dfwl[,"WINNER"])

for (i in 1:nrow(dfwl)) { 
if (dfwl$WINNER[i]=="HOME") dfwl$WINNER2[i]<-1
if (dfwl$WINNER[i]=="AWAY") dfwl$WINNER2[i]<-2}
```

```{r}
dfwl2<-cast(dfwl, HOME_TEAM ~ WINNER)
dfwl2<- dfwl2[,c(1,3,2)]
dfwl2$WIN_PCT<- round(dfwl2$HOME/(dfwl2$HOME+dfwl2$AWAY),2)

for (i in 1:nrow(dfwl2)) {
if(dfwl2$WIN_PCT[i]>0.5) dfwl2$HOMEADV[i]<- "YES" else dfwl2$HOMEADV[i]<- "NO"}

dfwl2<- dfwl2[order(dfwl2$WIN_PCT),]; dfwl2

library(ggplot2)
ggplot(dfwl2, aes(x=HOME_TEAM,y=WIN_PCT,col=HOMEADV))+ geom_point()
```
